# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.


```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
dictionary <- readr::read_csv(("green_dictionary.csv"))
green_data <- readr::read_csv(("green_data.csv"))
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?

Get the summaries of each data file     
```{r}
# dictionary %>% 
#   summarize(dictionary)
# 
# green_data %>% 
# summarize(green_data)
# fixed_green_data <- green_data %>% 
#                 na_if("-99")


# data_reversed <- c("green2",
#                    "comp6",
#                    "comp7",
#                    "comp8",
#                    "comp9",
#                    "comp10",
#                    "intel7",
#                    "intel8",
#                    "intel9",
#                    "intel10",
#                    "open7",
#                    "open8",
#                    "open9",
#                    "open10")
# 
# recoded_green_data <- fixed_green_data %>% 
#   mutate(across(all_of(data_reversed),
#                 ~ recode(.x, "1"= 5,"2" = 4,"4" = 2,"5"= 1 ),
#                 .names = "{.col}r") %>% 
#            select(recoded_green_data))


#Restarting everything because I couldn't figure out what was wrong.
print(green_data)

reversed <- c("green2", "comp6", "comp7", "comp8", "comp9", "comp10", 
              "intel7", "intel8", "intel9", "intel10", "open7", "open8", 
              "open9", "open10")

green_datar <- green_data %>% 
  mutate(across(all_of(reversed),
                ~ recode(.x, "1"= 5,"2" = 4,"4" = 2,"5"= 1 ),
                .names = "{.col}r"))

  


#There are -99 s in the data file that needs to be recoded
```
     
  2. Compute total scores for the four scales. 
     Recode variables as needed.
```{r}
green_datar %>% 
  rowwise() %>% 
  mutate(green_tot = sum(c_across(green1:green5), na.rm = TRUE),
         comp_tot = sum(c_across(comp1:comp10r), na.rm = TRUE),
         intel_tot = sum(c_across(intel1:intel10r), na.rm = TRUE),
         open_tot = sum(c_across(open1:open10r), na.rm = TRUE))
```
    
  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
```{r}
green_data_pomp <- green_datar %>% 
  mutate(across(c(green1:open10),
         ~ recode(.x, "1"= 0,"2" = 25, "3" = 50, "4" = 75,"5"= 100),
                .names = "{.col}_pomp"))

print(green_data_pomp)

Av_green_data_pomp <- green_data_pomp %>% 
  rowwise() %>% 
  mutate(green_av_pomp = mean(c_across(green1:green5), na.rm = TRUE),
         comp_av_pomp = mean(c_across(comp1:comp10r), na.rm = TRUE),
         intel_av_pomp = mean(c_across(intel1:intel10r), na.rm = TRUE),
         open_tav_pomp = mean(c_across(open1:open10r), na.rm = TRUE))

```
     
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
```{r}
Av_green_data_pomp %>% 
ggplot() +
  aes(comp_av_pomp,green_av_pomp) +
  geom_smooth(method = lm) 

Av_green_data_pomp %>% 
ggplot() +
  aes(comp_av_pomp,intel_av_pomp) +
  geom_smooth() 

Av_green_data_pomp %>% 
ggplot() +
  aes(comp_av_pomp,open_tav_pomp) +
  geom_smooth() 

Av_green_data_pomp %>% 
ggplot() +
  aes(open_tav_pomp,intel_av_pomp) +
  geom_smooth() 
```
  
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
```{r}

```
     
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.



