---
title: "Caliskan_finalproj"
author: "Neslihan Caliskan"
date: "5/1/2021"
output: 
  html_document: default
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading in datasets
```{r load in packages}
library(tidyverse)
library(readr)
library(ggplot2)
library(here)
library(ggdist)
```


```{r}
if ( !dir.exists( here::here("final_project", "data") ) ) {
  dir.create( here::here("final_project", "data", "output", ".R"), recursive = TRUE )
}

```

Loading in csv files
```{r load in csv files}
covid_prison_case <- read_csv(here("data", "covid_prison_cases.csv"))
                       
covid_prison_rate <- read_csv(here("data", "covid_prison_rates.csv"))
                       
covid_population <-  read_csv(here("data", "prison_populations.csv"))
                   
staff_population <-  read_csv(here("data", "staff_populations.csv"))

```


Renamed the column so the names for it wouldn't overlap across different datasets when I join them together.
```{r}
(staff_population %>% 
   rename(staff_april_pop = april_pop))

```

Joining all three datasets together
```{r}
# Merged_Covid_Data <- full_join(staff_population, covid_population, by = c("name", "abbreviation")) %>% 
#   full_join(covid_prison_case, by = c("name", "abbreviation"))

```

Filtering to see all the Florida data
```{r}
Florida_Data <- covid_prison_case %>% 
  filter(name == "Florida") %>% 
  select(as_of_date, total_staff_cases, total_staff_deaths, total_prisoner_cases, total_prisoner_deaths)
```


```{r}
Staff_Data_FL <- staff_population %>% 
   filter(name == "Florida") %>% 
    select(as_of_date, april_pop)

```


```{r}
Prisoner_Data_FL <- covid_population %>% 
   filter(name == "Florida") 
```


```{r}
ggplot(Florida_Data,
       aes(x = as.Date(as_of_date), 
           y= total_staff_cases),
           color = "purple",
           fill = "purple") +
  geom_point(alpha = 0.1) +
  scale_x_date("Date", date_breaks = "12 months", date_labels = "%m-%Y") +
  scale_y_discrete(name = "Total Staff Cases") +
  geom_smooth(method = "loess") +
  geom_vline(xintercept = as.numeric(as.Date("2020-01-01")), linetype = "dashed") +
  scale_y_continuous(name = "Total Staff Cases") +
  ggtitle("Total Staff Cases Per Year") +
  theme_bw() 

```


Compare prisoner cases to staff cases in Florida
```{r}
ggplot(Florida_Data,
       aes(x = total_prisoner_cases, 
           y= total_staff_cases)) +
  geom_point(alpha = 0.4,
             size = 6,
             color = "purple",
             fill = "purple") +
  scale_x_continuous(name = "Total Prisoner Cases") +
  scale_y_continuous(name = "Total Staff Cases") +
  ggtitle("Prisoner Cases over Staff Cases in Florida") +
  theme_classic() 
```


Compare prisoner deaths to staff deaths in Florida
```{r}
ggplot(Florida_Data,
       aes(x = total_prisoner_deaths, 
           y= total_staff_deaths)) +
  geom_point(alpha = 0.3,
             size = 3,
             color = "blue",
             fill = "blue") +
  scale_x_continuous(name = "Total Prisoner Deaths") +
  scale_y_continuous(name = "Total Staff Deaths") +
  ggtitle("Prisoner Deaths over Staff Deaths in Florida") +
  theme_minimal() 
```



Get the summary table for multiple columns in the dataset
```{r}
Summarized_Florida_Data <- Florida_Data %>% 
  summarise(TSC_MN = mean(total_staff_cases, na.rm = TRUE),
            TSC_SD = sd(total_staff_cases, na.rm = TRUE),
            TSD_MN = mean(total_staff_deaths, na.rm = TRUE),
            TSD_SD = sd(total_staff_deaths, na.rm = TRUE),
            TPC_MD = mean(total_prisoner_cases, na.rm = TRUE),
            TPC_SD = sd(total_prisoner_cases, na.rm = TRUE),
            TPD_MN = mean(total_prisoner_deaths, na.rm = TRUE),
            TPD_SD = sd(total_prisoner_deaths, na.rm = TRUE),
            TSC_min = min(total_staff_cases, na.rm = TRUE),
            TSD_min = min(total_staff_deaths, na.rm = TRUE),
            TPC_min = min(total_prisoner_cases, na.rm = TRUE),
            TPD_min = min(total_prisoner_deaths, na.rm = TRUE),
            TSC_max = max(total_staff_cases, na.rm = TRUE),
            TSD_max = max(total_staff_deaths, na.rm = TRUE),
            TPC_max = max(total_prisoner_cases, na.rm = TRUE),
            TPD_max = max(total_prisoner_deaths, na.rm = TRUE))
            
            
```



```{r}
