---
title: "Wrangling with Psych Data"
author: "Neslihan Caliskan"
date: "2/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Use the `psych::bfi` dataset.
2. Compute mean scores for each of the Big Five traits for each person.
3. Keep just Big Five scores, gender, age, and education.
4. Summarize the mean, standard deviation, minimum, and maximum values for the Big Five scores separately by gender groups.
5. Summarize the mean, standard deviation, minimum, and maximum values for the Big Five scores separately by educational level groups.

```{r Load in packages}
 library(tidyverse)
 library(dplyr)

```

Compute mean scores for each of the Big Five traits for each person.
```{r}
psych::bfi %>%
rowwise() %>%
mutate(A_tot = mean(c_across(A1:A5), na.rm = TRUE)) %>% 
mutate(C_tot = mean(c_across(C1:C5), na.rm = TRUE)) %>% 
mutate(E_tot = mean(c_across(E1:E5), na.rm = TRUE)) %>% 
mutate(O_tot = mean(c_across(O1:O5), na.rm = TRUE)) %>% 
mutate(N_tot = mean(c_across(N1:N5), na.rm = TRUE)) %>% 
select(A_tot, C_tot, E_tot, N_tot, O_tot)
```

 Keep just Big Five scores, gender, age, and education.
```{r}
bfiscore <- psych::bfi %>%
rowwise() %>%
mutate(A_tot = mean(c_across(A1:A5), na.rm = TRUE)) %>% 
mutate(C_tot = mean(c_across(C1:C5), na.rm = TRUE)) %>% 
mutate(E_tot = mean(c_across(E1:E5), na.rm = TRUE)) %>% 
mutate(O_tot = mean(c_across(O1:O5), na.rm = TRUE)) %>% 
mutate(N_tot = mean(c_across(N1:N5), na.rm = TRUE)) %>% 
select(A_tot, C_tot, E_tot, N_tot, O_tot, gender, age, education)
```

Summarize the mean, standard deviation, minimum, and maximum values for the Big Five scores separately by gender groups.
```{r}
bfiscore %>% 
  group_by(gender) %>% 
  summarize(
    across(A_tot:O_tot,
            list(mean = ~ mean(.x, na.rm = TRUE),
                 sd = ~ sd(.x, na.rm =TRUE),
                 min = ~ min(.x, na.rm = TRUE),
                 max = ~ max(.x, na.rm = TRUE))))
```

